### 2016-06-02 tasks_and_ideas.tex
adding tasks

\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.  This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.

@@

>>>>

\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.  This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.  (The previous ``double hashing'' construction seems clunky if you're going to assume you have a PRF and secret keys; is this just an example of people in one domain naively using a tool developed for another? )

@@

\item Speaking of the Niedermayer et al. attacks, these exploit the fact that there are different bloom filters for different record identifiers (i.e. one for last name, one for first name, one for city, etc.).  They propose various way to render their attacks useless, or at least very inefficient.  Can we actually prove something about one or more of the proposed countermeasures?
